Data Anonymization for Open Science: A Case Study

### 2025-05-14 submission_materials/article.tex
added missing citation and clarification of data requests

\hl{Although the data quality and utility was previously thoroughly explored, previous research on data privacy risks associated with non-traditional anonymization methods and synthetic data generation is rather sparse [BAYREM]. Few frameworks exist that can estimate residual privacy risks on anonymized and synthetic data alike. One of such framework is the Anonymeter framework by Giomi et al} \mycite{20} \hl{, originally proposed for large, synthetic datasets to evaluate risk of linkage, attribute inference and record singling-out.}

@@

The public repository at\mycite{18} contains all of the anonymized data used for this paper. Note that the original pseudonymized data from which the anonymized data was derived is considered personal data and is therefore not publicly available.  \hl{Please contact Bojan Leskosek (bojan.Leskosek@fsp.uni-lj.si). This data may be used for the purpose of studying anonymity, either by sharing the data or by running the anonymization software locally.}

@@

>>>>

\hl{Although the data quality and utility was previously thoroughly explored, previous research on data privacy risks associated with non-traditional anonymization methods and synthetic data generation is rather sparse} \mycite{35} \hl{. Few frameworks exist that can estimate residual privacy risks on anonymized and synthetic data alike. One of such framework is the Anonymeter framework by Giomi et al} \mycite{20} \hl{, originally proposed for large, synthetic datasets to evaluate risk of linkage, attribute inference and record singling-out.}

@@

The public repository at\mycite{18} contains all of the anonymized data used for this paper. Note that the original pseudonymized data from which the anonymized data was derived is considered personal data and is therefore not publicly available.  \hl{Please contact Bojan Leskosek (bojan.Leskosek@fsp.uni-lj.si) or Gregor Jurak (gregor.jurak@fsp.uni-lj.si) to access the original dataset. Any data access request should state the purpose for requesting the data, describe measures how sensitive data will be protected and assurance of ethical use. Requesters need to sign a Data Use Agreement (DUA). We guarantee that reasonable requests will be honored. This data may be used for the purpose of studying anonymity, either by sharing the data or by running the anonymization software locally.}

@@

%35
\bibitem{kaabachi2025review}
\bibinfo{author}{Kaabachi, B.},
\bibinfo{author}{Despraz, J.}, 
\bibinfo{author}{Meurers, T.}, 
\bibinfo{author}{Otte, K.}, 
\bibinfo{author}{Halilovic, M.}, 
\bibinfo{author}{Kulynych, B.}, 
\bibinfo{author}{Prasser, F.}, 
\bibinfo{author}{Raisaro, J. L.}
\newblock \bibinfo{journal}{\bibinfo{title}{A scoping review of privacy and utility metrics in medical synthetic data}}.
\newblock {\emph{\JournalTitle{npj Digital Medicine}}} \textbf{\bibinfo{volume}{8}} (\bibinfo{year}{2025}).
